Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-24 main.tex
tweaked intro

In this paper we advance the idea that combinatorial proofs can provide
a notion of proof identity for first order logic. \emph{First-order
combinatorial proofs} were introduced by Hughes in~\cite{hughes:fopws}.
However, even though Hughes proves soundness and completeness, the 
proof is unsatisfactory: (1) the soundness argument is long and
cumbersome, and (2) the completeness proof does not allow a syntactic
proof to be read back from a combinatorial proof. In fact, there is the
fundamental problem that not all combinatorial proofs can be obtained
as translations of sequent calculus proofs.

>>>>

In this paper we advance the idea that combinatorial proofs can provide
a notion of proof identity for first-order logic. \emph{First-order
combinatorial proofs} were introduced by Hughes in~\cite{hughes:fopws}.
For example, a first-order combinatorial proof of Smullyan's 
``drinker paradox'' $\drinkerformula$ is shown above-right.
However, even though Hughes proves soundness and completeness, the 
proof is unsatisfactory: (1) the soundness argument is extremely long,
intricate and cumbersome, and (2) the completeness proof does not allow
a syntactic
proof to be read back from a combinatorial proof. In fact, there is the
fundamental problem that not all combinatorial proofs can be obtained
as translations of sequent calculus proofs.
